---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# robodeck <a href="https://jonthegeek.github.io/robodeck/"><img src="man/figures/logo.svg" align="right" height="240" alt="robodeck website" /></a>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/robodeck)](https://CRAN.R-project.org/package=robodeck)
[![Codecov test coverage](https://codecov.io/gh/jonthegeek/robodeck/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jonthegeek/robodeck?branch=main)
[![R-CMD-check](https://github.com/jonthegeek/robodeck/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jonthegeek/robodeck/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Sometimes it's easier to *edit* a deck than to *create* one from scratch.
Enter robodeck!

This extremely experimental package uses the [OpenAI API](https://platform.openai.com/docs/api-reference/) to generate Quarto slide decks quickly.

## Installation

You can install the development version of robodeck from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jonthegeek/robodeck")
```

## Usage

We do not recommend using the output of this package without editing.
That said, the deck below was generated without editing, as an example.

```{r full-deck}
library(robodeck)
description <- 
  "robodeck is an R package that utilizes the OpenAI API 
   (https://platform.openai.com/docs/api-reference/) to quickly generate Quarto 
   slide decks. In this lightning talk I will demonstrate how to use 
   robodeck::gen_deck() to automatically generate a slide deck from just a title 
   and description, and why you should carefully edit the results!" |> 
  stringr::str_squish()

# Store an API key in an environment variable called OPENAI_API_KEY.

deck_markdown <- gen_deck(
  title = "Introducing robodeck",
  description = description,
  minutes = 5
)
```

```{r full-deck-result, echo=FALSE}
paste("| ", stringr::str_split_1(deck_markdown, "\n")) |> 
  cat(sep = "\n")
```

Note that function calls will hit the OpenAI API, which is not free.
At the time of this writing, experiments with the API while writing this package have incurred a total cost of about $0.13, almost all of that while experimenting with the more expensive "GPT-4-turbo" API.
By default, robodeck uses the "GPT-3.5-turbo" API, which should cost <$0.01 to generate a deck.

## Code of Conduct

Please note that the robodeck project is released with a [Contributor Code of Conduct](https://jonthegeek.github.io/robodeck/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
